---
title: "RPlots_HurricaneIsland"
author: "Connor McCoy"
date: "11/13/2019"
output: 
  html_document:
    theme: cosmo
    code_folding: hide
    toc: yes
---
*** 
### SUMMARY

In this document, the team has started to create plots based on the different questions regard the dataset provided by the Hurricane Island Scallop Project. These plots will aid us in visualizing the comparison of data relevant to the research questions. The research questions which we are focusing in this project are:

  * What is the relation of environmental temperature to scallop size (Shell height, meat weight, viscera weight, etc.)?
  * How gear types impact the growth of scallops?
  * Differences in growth rate of Male and Female scallops?
  * How is temperature gradient over two years?
  * What is the temperature difference between surface temperature and cage bottom temperature?
  * How do the top temperature and intensity vs bottom temperature and intensity differ?
  * How do temperature and light intensity affect the GSI and what is the contribution of gear type in this?


### STEPS INVOLVED IN STATISTICAL ANALYSIS

  * Install libraries
```{r libraries}
library(tidyverse)
library(reshape2)
library(ggplot2)
```

  * Read the data from the csv file into the dataframe GSI_Data_Sheet_cleaned.
```{r GSI_Data_Sheet_cleaned}
GSI_Data_Sheet_cleaned <- read_csv("GSI_Data_Sheet_cleaned.csv")
```



#### 2. Differences in growth rate of scallops in different cages
  * These steps create a bar chart that compares the different types of weight measurements across the cage types that they were kept in:

  * Summarise means of the different categories of weight, grouped by cage type.
```{r gear_GSI}
gear_GSI <- GSI_Data_Sheet_cleaned %>% group_by(Gear.Type) %>% summarise(GSI = mean(GSI), Viscera = mean(Total.Viscera.Weight.), Meat = mean(Meat.Weight.), Gonad = mean(Gonad.Weight.), Shell = mean(Shell.Weight., na.rm = TRUE))
```

  * Melt data into a format compatible with ggplot, grouped by "Gear.Type"
```{r gear_GSI_long}
gear_GSI_long <- melt(gear_GSI, id = "Gear.Type")
```

  * Create plot of data, store in global variable
```{r gear_plot}
gear_plot <- ggplot(gear_GSI_long, aes(Gear.Type, value)) + geom_bar(aes(fill = variable), position = "dodge", stat = "identity")
```

  * Add labels to graph
```{r }
gear_plot + labs(x= "Gear Type", y = "Weight (grams)", fill = "Weight Type")
```
  

#### 3. Differences in growth rate of Male and Female scallops
  * These steps create a bar chart that compares the different types of weight measurements across gender:
  
  * Summarise means of the different categories of weight, grouped by Sex.
```{r sex_GSI}
sex_GSI <- GSI_Data_Sheet_cleaned %>% group_by(Sex) %>% summarise(GSI = mean(GSI), Viscera = mean(Total.Viscera.Weight.), Meat = mean(Meat.Weight.), Gonad = mean(Gonad.Weight.), Shell = mean(Shell.Weight., na.rm = TRUE))
```

  * Melt data into a format compatible with ggplot, grouped by "Sex"
```{r sex_GSI_long}
sex_GSI_long <- melt(sex_GSI, id = "Sex")
```

  * Create plot of data, store in global variable
```{r sex_plot}
sex_plot <- ggplot(sex_GSI_long, aes(Sex, value)) + geom_bar(aes(fill = variable), position = "dodge", stat = "identity")
```

  * Add labels to graph
```{r }
sex_plot + labs(y = "Weight (grams)", fill = "Weight Type")
```

#### 4. Temperature gradient over 2 years (2017 - 2019)
  * These steps create a line graph that shows the temperature over 2017 till 2019.

  * Read the csv file with column type
```{r cagetemp}
cagetemp <- read_csv("Copy_of_Cage_5_2017_2019_cleaned.csv", col_types = cols(Date.Time = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
```

  * Average of the temperature by each day
```{r tempavg}
tempavg <- setNames(aggregate(cagetemp$`Temp...#20178444`, by=list(cagetemp$Date.Time), mean), c("Date", "Avg_temp"))
```

  * Create plot of data
```{r temp_plot}
ggplot(data = tempavg,mapping=aes(x=Date,y=Avg_temp)) + geom_point() + geom_smooth()
```

#### 5. Temperature and Intensity difference in Net top and Net Bottom

  * These steps create a line graph to show differences in temperature and intensity in Net top and Net bottom.
  
  * Read the data from the csv file into the dataframe Copy_of_Net_5_Top_GSI_Top_cleaned.
```{r Copy_of_Net_5_Top_GSI_Top_cleaned}
Copy_of_Net_5_Top_GSI_Top_cleaned <- read_csv("Copy_of_Net_5_Top_GSI_Top_cleaned.csv", col_types = cols(`Date.Time.GMT.-0400` = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
```

  * Generate the average temperature per day for Net Top
```{r avg_temp_net5_top_GSI}
Copy_of_Net_5_Top_GSI_Top_cleaned$`Date.Time.GMT.-0400` <- as.Date(Copy_of_Net_5_Top_GSI_Top_cleaned$`Date.Time.GMT.-0400`)
Net5TopAverage <- setNames(aggregate(Copy_of_Net_5_Top_GSI_Top_cleaned$`Temp.°F`, by=list(Copy_of_Net_5_Top_GSI_Top_cleaned$`Date.Time.GMT.-0400`), mean), c("Date", "Avg_temp_top"))
```

  * Structure of dataframe Net5TopAverage
```{r str_net5topavg}
str(Net5TopAverage)
```

  * Summary of dataframe Net5TopAverage
```{r summary Net5TopAverage}
summary(Net5TopAverage)
```
 * Read the data from the csv file into the dataframe Copy_of_Net_5_Bottom_GSI_2019_cleaned.
```{r Copy_of_Net_5_Bottom_GSI_2019_cleaned}
Copy_of_Net_5_Bottom_GSI_2019_cleaned <- read_csv("Copy_of_Net_5_Bottom_GSI_2019_cleaned.csv", col_types = cols(`Date.Time.GMT.-0400` = col_datetime(format = "%Y-%m-%d %H:%M:%S")))
```

  * Generate the average temperature per day for Net Bottom
```{r avg_temp_net5_bottom_GSI}
Copy_of_Net_5_Bottom_GSI_2019_cleaned$`Date.Time.GMT.-0400` <- as.Date(Copy_of_Net_5_Bottom_GSI_2019_cleaned$`Date.Time.GMT.-0400`)

Net5BottomAverage <- setNames(aggregate(Copy_of_Net_5_Bottom_GSI_2019_cleaned$`Temp.°F`, by=list(Copy_of_Net_5_Bottom_GSI_2019_cleaned$`Date.Time.GMT.-0400`), mean), c("Date", "Avg_Temp_bottom"))
```

  * Structure of dataframe Net5BottomAverage
```{r str_net5botavg}
str(Net5BottomAverage)
```

  * Summary of dataframe Net5BottomAverage
```{r summary Net5BottomAverage}
summary(Net5BottomAverage)
```
* Merge the dataframes.
```{r Net5TopVsBottom}
Net5TopVsBottom = setNames(merge(Net5TopAverage,Net5BottomAverage, by="Date"), c("Date", "Avg_temp_Top", "Avg_temp_bottom"))
```

  * Structure of dataframe Net5TopVsBottom
```{r str_net5TopVsBottom}
str(Net5TopVsBottom)
```

  * Summary of dataframe Net5TopVsBottom
```{r summary Net5TopVsBottom}
summary(Net5TopVsBottom)
```
  
  * Melt data of the Temperature
```{r Net5TopVsBottom_long}
Net5TopVsBottom_long <- melt(Net5TopVsBottom, id = "Date")
```

  * Create plot of data, store in global variable for temperature
```{r temp_avg}
ggplot(data = Net5TopVsBottom_long, mapping = aes(x= Date, y= value, color = variable))+
geom_line()+
geom_text(data = Net5TopVsBottom_long %>% group_by(variable) %>% filter(value== max(value)), aes(label= variable, x= Date,y= value,size = 3, hjust = 0))+
labs(x= "Date",y="Temperature")+
ggtitle("Net5 top temp vs bottom temp")
```
  
   * Generate the average intensity per day.
```{r avg_int_net5_top_GSI}
Net5TopAverageInt <- setNames(aggregate(Copy_of_Net_5_Top_GSI_Top_cleaned$`Intensity..lum/ft²`, by=list(Copy_of_Net_5_Top_GSI_Top_cleaned$`Date.Time.GMT.-0400`), mean), c("Date", "Avg_int_top"))
```

  * Structure of dataframe Net5TopAverage
```{r str_net5topavgInt}
str(Net5TopAverageInt)
```

  * Summary of dataframe Net5TopAverage
```{r summary Net5TopAverageInt}
summary(Net5TopAverageInt)
```

  * Generate the average Intensity per day at Bottom.
```{r avg_temp_net5_bottom_GSI_int}
Net5BottomAverageInt <- setNames(aggregate(Copy_of_Net_5_Bottom_GSI_2019_cleaned$`Intensity..lum/ft²`, by=list(Copy_of_Net_5_Bottom_GSI_2019_cleaned$`Date.Time.GMT.-0400`), mean), c("Date", "Avg_Temp_bottom"))
```

  * Structure of dataframe Net5TopAverage
```{r str_net5botavgInt}
str(Net5BottomAverageInt)
```

  * Summary of dataframe Net5TopAverage
```{r summary Net5BottomAverageInt}
summary(Net5BottomAverageInt)
```
* Merge the dataframes.
```{r Net5TopVsBottomInt}
Net5TopVsBottomInt = setNames(merge(Net5TopAverageInt,Net5BottomAverageInt, by="Date"), c("Date", "Avg_Intensity_Top", "Avg_Intensity_bottom"))
```

  * Structure of dataframe Net5TopVsBottom of Intensity
```{r str_net5TopVsBottomInt}
str(Net5TopVsBottomInt)
```

  * Summary of dataframe Net5TopVsBottom of Intensity
```{r summary Net5TopVsBottomInt}
summary(Net5TopVsBottomInt)
```

 * Melt data of the Intensity
```{r Net5TopVsBottomInt_long}
Net5TopVsBottomInt_long <- melt(Net5TopVsBottomInt, id = "Date")
```

  * Create plot of data, store in global variable for intensity
```{r Int_avg}
ggplot(data = Net5TopVsBottomInt_long, mapping = aes(x= Date, y= value, color = variable))+
geom_line()+
geom_text(data = Net5TopVsBottomInt_long %>% group_by(variable) %>% filter(value== max(value)), aes(label= variable, x= Date,y= value,size = 3, hjust = 0))+
labs(x= "Date",y="Intensity")+
ggtitle("Net5 top Intensity vs bottom Intensity")
```


### CONTRIBUTION STATEMENT
* The work for this assignment was distributed as follows:

  * Connor McCoy
    1. Created graph for Cage Vs Weight Comparison
    2. Created graph for Sex Vs Weight Comparison
    3. Created RMarkdown document.

* As the role of the Proof Reader is alternating for every assignment, Connor McCoy fulfilled the role of Proof Reader for the RScript Documentation.
